The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with {\em Gaia} Data and Beyond

### 2019-04-25 paper/ms.tex
Add justification for spec. eq

In the remainder of this section, we compare our analytic estimates of the effect on actions of a midplane offset against numerical calculations. The effect of velocity offsets on actions is deferred to future work, as we discuss in Section~\ref{ssec:lsr_var}.

@@

In each panel of Figure~\ref{fig:many_orbit_wrong_ref}, where relevant, we
include the estimation of the action errors derived under the epicyclic
approximation in Section~\ref{ssec:epi_action}. Note that we consider an error
in the $x$-coordinate $\Delta x$, which is not quite the same as $\Delta R$.
For observations of stars close to us, we have that $\Delta x \sim \Delta R$,
but for the experiment performed in this Section we consider observations of
the star throughout its entire orbit. This introduces a factor of $2/\pi$ when
converting from $\Delta R$ to $\Delta x$, which we derive in
Appendix~\ref{app:deltax}.

@@

An offset $\Delta x$ results in an erroneous radius $R_{\text{err}}$ related by
the formula,
\beq
(x+\Delta x)^2 + y^2 = R_{\text{err}}^2\text{.}
\eeq
Keeping only terms to first order in $\Delta x$, we have that,
\beq
\begin{split}
R_{\text{err}}^2 &= R^2 - 2 R \cos{\theta} \Delta x \\
\implies \Delta R &\equiv \abs{R_{\text{err}} - R} = \abs{\cos{\theta}} \Delta x\text{.}
\end{split}
\eeq
Averaging over the circle, we therefore have that,
\beq
\avg{\Delta R} = \frac{2}{\pi} \Delta x\text{.}
\eeq

>>>>

In the remainder of this section, we compare our analytic estimates of the effect on actions of a midplane offset against numerical calculations. Detailed worked on the effect of velocity offsets on actions is deferred to future work, as we discuss in Section~\ref{ssec:lsr_var}.

@@

In each panel of Figure~\ref{fig:many_orbit_wrong_ref}, where relevant, we
include the estimation of the action errors derived under the epicyclic
approximation from Equation~\ref{eq:Ji_err_mosttime}. This Equation is relevant since during most of the orbit the star will be at maximum radial and vertical amplitude and we do not consider velocity offsets. Note that we consider an error
in the $x$-coordinate $\Delta x$, which is not quite the same as $\Delta R$.
For observations of stars close to us, we have that $\Delta x \sim \Delta R$,
but for the experiment performed in this Section we consider observations of
the star throughout its entire orbit. This introduces a factor of $2/\pi$ when
converting from $\Delta R$ to $\Delta x$, which we derive in
Appendix~\ref{app:deltax}.

@@

An offset $\Delta x$ results in an erroneous radius $R_{\text{err}}$ related by
the formula,
\beq
(x+\Delta x)^2 + y^2 = R_{\text{err}}^2\text{.}
\eeq
Keeping only terms to first order in $\Delta x$, we have that,
\beq
\begin{split}
R_{\text{err}}^2 &= R^2 - 2 R \cos{\phi} \Delta x \\
\implies \Delta R &\equiv \abs{R_{\text{err}} - R} = \abs{\cos{\phi}} \Delta x\text{.}
\end{split}
\eeq
Averaging over the circle, we therefore have that,
\beq
\avg{\Delta R} = \frac{2}{\pi} \Delta x\text{.}
\eeq
